Embedding intuitionistic into classical logic

### 2022-07-13 Notes/Embedding intuitionistic into classical logic/EIICL.tex
Removed indices

	\subsection{Equivalid normalization}

	Now trying to apply Herbrandization to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. A similar translation was proposed in~\cite{statman1979intuitionistic}.

	\begin{definition}
		Let $\varphi$ be some formula. For each sub(semi)formula $\psi$ of $\varphi$ consider some new $n$-ary relation symbol $P_\psi$ where $n$ is the number of variables occurring in $\psi$ that is not quantified within $\psi$. We denote those variables with $\vec t_\psi$ in some arbitrary but fixed order. We inductively define clause sets $\mathcal S^+(\varphi)$ and $\mathcal S^-(\varphi)$ as follows:
		\begin{itemize}
			\item For every atomic formula $A$\\$\mathcal S^+(A) = \{P_A(\vec t_A)\to A\}$\\$\mathcal S^-(A) = \{A\to P_A(\vec t_A)\}$
			\item For every conjunction or disjunction $\varphi\circ\psi$ with $\circ\in\{\wedge,\vee\}$\\$\mathcal S^+(\varphi\circ\psi) = \{P_{\varphi\circ\psi}(\vec t_{\varphi\circ\psi})\to P_{\varphi}(\vec t_\varphi)\circ P_{\psi}(\vec t_\psi)\}\cup \mathcal S^+(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\circ\psi) =\{P_{\varphi}(\vec t_\varphi)\circ P_{\psi}(\vec t_\psi)\to P_{\varphi\circ\psi}(\vec t_{\varphi\circ\psi})\}\cup \mathcal S^-(\varphi)\cup \mathcal S^-(\psi)$
			\item For every implication $\varphi \to\psi$\\$\mathcal S^+(\varphi\to\psi) = \{(P_{\varphi\to\psi}(\vec t_{\varphi\to\psi})\wedge P_{\varphi}(\vec t_\varphi))\to P_{\psi}(\vec t_\psi)\}\cup \mathcal S^-(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\to\psi)  = \{(P_{\varphi}(\vec t_\varphi)\to P_{\psi}(\vec t_\psi))\to P_{\varphi\to\psi}(\vec t_{\varphi\to\psi})\}\cup \mathcal S^+(\varphi)\cup \mathcal S^-(\varphi)$
			\item For quantified formulas $Qx\varphi(x)$ with $Q\in \{\forall,\exists\}$\\$\mathcal S^+(Qx\varphi(x)) = \{P_{Qx\varphi}(\vec t_{Qx\varphi})\to QxP_{\varphi}(\vec t_{\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^+(\varphi)\}$\\$\mathcal S^-(Qx\varphi(x))  = \{QxP_{\varphi}(\vec t_{\varphi})\to P_{Qx\varphi}(\vec t_{Qx\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^-(\varphi)\}$
		\end{itemize}
		and have $\mathcal S(\varphi) = \mathcal S^+(\varphi)\cup\mathcal S^-(\varphi)$.
	\end{definition}

@@

	\begin{definition}
		For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms $P_\psi$. By slight abuse of notation we mean with $\vec t_\psi$ elements of the domain instead of variables. In the classical case have	
		$$P_{\varphi\wedge\psi}^I(\vec t_{\varphi\wedge\psi}) \Leftrightarrow P_{\varphi}^I(\vec t_\varphi)\wedge P_{\psi}^I(\vec t_\psi)\indent P_{\varphi\vee\psi}^I(\vec t_{\varphi\vee\psi}) \Leftrightarrow P_{\varphi}^I(\vec t_\varphi)\vee P_{\psi}^I((\vec t_\psi))$$$$ P_{\varphi\to\psi}^I(\vec t_{\varphi\to\psi}) \Leftrightarrow (\neg P_{\varphi}^I(\vec t_{\varphi}))\vee P_{\psi}^I(\vec t_{\psi})$$
		$$P_{\forall x\varphi}^I(\vec t_{\forall x\varphi}) \Leftrightarrow \{\vec t\:|\:\:P_{\varphi}^I(\vec t_\varphi) \text{ for all $x\in M$}\}$$$$ P_{\exists x\varphi}^I(\vec t_{\exists x\varphi}) \Leftrightarrow \{\vec t\:|\:\:P_{\varphi}^I(\vec t_\varphi) \text{ for some $x\in M$}\}$$
		\\

		and for intuitionistic logic and some world $u$ 		
		$$P_{\varphi\wedge\psi}^{I_u}(\vec t_{\varphi\wedge\psi}) \Leftrightarrow P_{\varphi}^{I_u}(\vec t_\varphi)\wedge P_{\psi}^{I_u}(\vec t_\psi)\indent P_{\varphi\vee\psi}^{I_u}(\vec t_{\varphi\vee\psi}) \Leftrightarrow P_{\varphi}^{I_u}(\vec t_\varphi)\vee P_{\psi}^{I_u}((\vec t_\psi))$$$$ P_{\varphi\to\psi}^{I_u}(\vec t_{\varphi\to\psi}) \Leftrightarrow(\neg P_{\varphi}^{I_w}(\vec t_{\varphi}))\vee P_{\psi}^{I_w}(\vec t_{\psi})\text{ for all $w\geq u$}$$
		$$P_{\forall x\varphi}^{I_u}(\vec t_{\forall x\varphi}) \Leftrightarrow P_{\varphi}^{I_w}(\vec t_\varphi) \text{ for all $w\geq u$, $x\in M_w$}$$$$ P_{\exists x\varphi}^{I_u}(\vec t_{\exists x\varphi}) \Leftrightarrow P_{\varphi}^{I_u}(\vec t_\varphi) \text{ for some $x\in M_u$}$$
		\\
	\end{definition}

@@

	\begin{lemma}
		For every formula $\varphi$ and structure $\mathcal M$
		$$\mathcal S(\mathcal M, \varphi)\models\mathcal S(\varphi)$$
	\end{lemma}

@@

	\begin{corollary}\label{equivalid}
		In both intuitionistic and classical logic
		\begin{itemize}
			\item $\varphi$ is satisfiable iff $\mathcal \bigwedge S^+(\varphi)\wedge P_\varphi(\vec t_\varphi)$ is. 
			\item $\varphi$ is valid iff $\bigwedge\mathcal S^-(\varphi)\to P_\varphi(\vec t_\varphi)$ is.
		\end{itemize}
	\end{corollary}

	\subsection{IPC to CPC}

@@

	\subsection{IPC to QBF}

	It is well known that a polynomial time translation between QBF and IPC must exists, since both problems are PSPACE complete~\cite{garey1979computers, statman1979intuitionistic}. However giving an explicit translation from IPC to QBF can still be useful as good solvers exists for QBF but for IPC not so much. Furthermore we will be able to give fragments of IPC for which validity is complete for other stages of the polynomial hierarchy. The translation from the last section will serve as a useful tool for this. We will not explain the semantics of QBF in depth. Intuitively just think that the interpretation of existentially quantified variables may depend on variables quantified above them.

	 Fix some set $\mathcal S$ of formulas $\psi$ of the form $$\hspace*{-.7cm}A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$and a formula $$\varphi = \bigwedge \mathcal S\to P$$
	and denote with $\mathcal F_\to$ the set of formulas of the form $(A\to B)\to C$. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a linear-size formula is: Instead of expressing validity at every node of $\mathcal M_T$ - which was done in the CPC translation - we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $F_\psi$ in the next definition handle the branching, i.e. express which path is considered.

	\begin{definition}
		For every propositional variable $X$ occurring in $\mathcal S$ and non-negative integer $n$ consider a new atom $X^n$ and for every formula $\psi\in\mathcal F_\to$ consider a new atom $F_\psi^n$. Let $\vec X^n$ range over all propositional variables $X^n$ and $\vec F^n$ range over all $F_\psi^n$. Define
		\begin{itemize}
			\item valid$(n)$ which encodes that $\vec F^n_\psi$ represents a valid next element of a sequence without repetition, i.e. if we interpret the $\vec F^i$ as bit-vectors, then $\vec F^n$ has exactly one bit set to $1$, indicating the formula at the $n$-th position of the sequence, and it is at a position that is $0$ in $\sum\{\vec F^i\:|\:i < n\}$.
			\item per($n$) which encodes that the persistency condition holds.
			\item sat$_{\mathcal S}(n)$ encoding that the formulas in $\mathcal S\setminus\mathcal F_\to$ hold at the $n$-th world of the path.
			\item sat$_{\mathcal F_\to}(n)$ encoding that the formula in $\mathcal F_\to$ that is represented by $\vec F^{n-1}$ holds.
		\end{itemize}
		Have $k = |\mathcal F_\to|$ and define
		$$\varphi^Q_{k} = \exists \vec X^k\left(\text{per}(k)\wedge \text{sat}_{\mathcal S}(k)\wedge \text{sat}_{\mathcal F_\to}(k)\right)$$
		for $0 < i < k$
		$$\hspace*{-.8cm}\varphi^Q_{i} = \exists \vec X^i\forall \vec F^i\left(\text{per}(i)\wedge \text{sat}_{\mathcal S}(i)\wedge \text{sat}_{\mathcal F_\to}(i)\wedge\left(\text{valid}(i)\to \varphi^Q_{i+1}\right)\right)$$
		and $$\varphi^Q = \varphi_0^Q = \exists \vec X^0\forall \vec F^0\left(\neg P^0\wedge \text{sat}_{\mathcal S}(0)\wedge(\text{valid}(0)\to \varphi_1^Q)\right)$$
		Example encodings of the above formulas would be
		\begin{align*}
			\text{valid}(n) = &\left(\bigvee \{\mathcal F^n_\psi\:|\:\psi\in\mathcal F_\to\}\right)\wedge\left(\bigwedge \{\neg(F^n_{\psi_1}\wedge F^n_{\psi_1})\:|\:\psi_1\neq\psi_2\in\mathcal F_\to\}\right)\wedge\\&\wedge\left(\bigwedge\left\{\bigwedge\{F^i_\psi\to\neg F^n_\psi\:|\:i < n\}\:|\:\psi\in\mathcal F_\to\right\}\right)\\
			\text{per}(n) = & \bigwedge\{X^{n-1}\to X^n\:|\: X \text{ prop. variable with }X^{n-1}\in\vec X^{n-1}, X^n \in\vec X^{n}\}\\
			\text{sat}_{\mathcal S}(n) = &\bigwedge\left\{(A^n\circ B^n)\to C^n\:|\:(A\circ B)\to C\in \mathcal S\setminus\mathcal F_\to\right\}\wedge\\
			&\bigwedge\left\{A^n\to (B^n\circ C^n)\:|\:A\to (B\to C)\in \mathcal S\setminus\mathcal F_\to\right\}\\
			\text{sat}_{\mathcal F_\to}(n) = & \bigwedge\{F^{n-1}_\psi\to (A^n\to B^n)\to C^{n-1}\:|\:\psi = (A\to B)\to C\in\mathcal F_\to\}
		\end{align*}
	\end{definition}

@@

	As a final result we would like to prove that the above problems are complete for their respective complexity classes. It is sufficient to provide a polynomial reduction from QBF with bounded number of quantifier alternation to them. Such translations exists~\cite{statman1979intuitionistic,vsvejdar2003polynomial}, however they are insufficient in that they generate more formulas of form $(A\to B)\to C$ than there are quantifier alternations. We therefore would need a slightly new translation.

	\section{Predicate logic}

	We now give an analogous transformation for first order logic. However our trick of lifting the sentence to first-order logic to encode the Kripke semantics no longer works in such a straightforward manner, since we already are in first-order logic. However we do it nonetheless! The domain of our classical model will feature on the one hand elements representing worlds in a Kripke frame and on the other hand the domain-elements from the Kripke model. We reconcile these notions by introducing a special binary predicate $E$, first considered in~\cite{baaz2006skolemization} and expanded onto in~\cite{iemhoff2010eskolemization}, where $E(x, u)$ encodes that $x$ is an element of the domain of the world $u$. In addition we use a unary predicate $W$ that encodes that an element represents a world.

	\subsection{CQC to IQC}

	First of all recall that due to~\ref{equivalid} it is sufficient to consider sentences of the form $\bigwedge\mathcal S\to P$ where all $\psi\in\mathcal S$ are of one of the forms

	$$\forall \vec t(A(\vec t_{A})\to (B(\vec t_B)\wedge C(\vec t_C))), \forall \vec t((A(\vec t_{A})\wedge B(\vec t_B))\to C(\vec t_C)),$$$$ \forall \vec t(A(\vec t_{A})\to (B(\vec t_B)\vee C(\vec t_C))),
	\forall \vec t((A(\vec t_{A})\vee B(\vec t_B))\to C(\vec t_C)),$$$$ \forall \vec t((A(\vec t_A)\to B(\vec t_B))\to C(\vec t_C)),\forall \vec t(\forall xA(\vec t_A)\to B(\vec t_B)),$$$$ \forall \vec t(A(\vec t_A)\to\forall xB(t_B)), \forall \vec t(\exists xA(\vec t_A)\to B(\vec t_B)), \forall \vec t(A(\vec t_A)\to\exists xB(t_B))$$	
	First let us note how we axiomatize $E$ and $W$. For a vector $\vec x = x_1\dots x_n$ we define $\vec E(\vec x, u) = \bigwedge\{E(x_i, u)\:|\:i\leq n\}$.
	\begin{align*}
		E(\varphi) = & \forall u\forall x(E(x, u)\to(\neg W(x)\wedge W(u)))\wedge\\
		 & \forall u\forall w\forall x((E(x, u)\wedge u\preceq w)\to E(x, w))\wedge\\
		 & \bigwedge\{\forall\vec t\forall u(\vec E(\vec t, u)\to E(f(\vec t), u))\:|\:\text{$f$ is an $n$-ary function symbol}\}
	\end{align*}
	The one possible problem in this encoding is that we have a global interpretation of function symbols, i.e. in an intuitionistic model we could have worlds $u, v$ such that $f^{I_u}\neq f^{I_v}$. However this is not a problem: We can take as the domain of our classical model equivalence classes $\{[(x, u)]\:|\: x\in M_u\}$ under the relation $(x, u)\sim (y, v)$ iff $x = y$ and there exists $w$ comparable with $u, v$ such that $x\in w$ and interpret $f^I([x, u]) = [f^{I_u}(x), u]$. Then our classical translation only forces functions to be equal on arguments on which they must be equal anyway. So the Kripke model does in fact not afford us any additional generality.

	As before we need to axiomatize $\preceq$. For each $n$-ary relation symbol consider $P$ a new $n+1$ ary relation symbol $P^\#$.  The only difference in that for persistence we may require additional quantification. 
	\begin{align*}
		K(\varphi) = & \forall k(k\preceq k)\wedge \forall k\forall l((k\preceq l\wedge l\preceq k)\to l = k)\wedge\\
		& \forall k\forall l\forall m((k\preceq l\wedge l\preceq m)\to k\preceq m)\wedge\\
		& \bigwedge\{\forall k\forall l(k\preceq l\to \forall \vec x(A^\#(\vec x, k)\to A^\#(\vec x, l)))\:|\:\text{$A$ occurs in $\varphi$}\}
	\end{align*}
	Using $E$ and $W$ we obtain a set $\mathcal S^\circ$ by including formulas as follows:

>>>>

	\section{Equivalid normalization}

	Of course transforming a propositional formula into a predicate formula is somewhat unsatisfying. As a first step we want to apply Herbrandization. Now trying to apply it to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. A similar translation was proposed in~\cite{statman1979intuitionistic}.

	\begin{definition}
		Let $\varphi$ be some formula. For each sub(semi)formula $\psi$ of $\varphi$ consider some new $n$-ary relation symbol $P_\psi$ where $n$ is the number of variables occurring in $\psi$ that is not quantified within $\psi$. We denote those variables with $\vec z_\psi$ in some arbitrary but fixed order. We inductively define clause sets $\mathcal S^+(\varphi)$ and $\mathcal S^-(\varphi)$ as follows:
		\begin{itemize}
			\item For every atomic formula $A$\\$\mathcal S^+(A) = \{P_A(\vec z_A)\to A\}$\\$\mathcal S^-(A) = \{A\to P_A(\vec z_A)\}$
			\item For every conjunction or disjunction $\varphi\circ\psi$ with $\circ\in\{\wedge,\vee\}$\\$\mathcal S^+(\varphi\circ\psi) = \{P_{\varphi\circ\psi}(\vec z_{\varphi\circ\psi})\to P_{\varphi}(\vec z_\varphi)\circ P_{\psi}(\vec z_\psi)\}\cup \mathcal S^+(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\circ\psi) =\{P_{\varphi}(\vec z_\varphi)\circ P_{\psi}(\vec z_\psi)\to P_{\varphi\circ\psi}(\vec z_{\varphi\circ\psi})\}\cup \mathcal S^-(\varphi)\cup \mathcal S^-(\psi)$
			\item For every implication $\varphi \to\psi$\\$\mathcal S^+(\varphi\to\psi) = \{(P_{\varphi\to\psi}(\vec z_{\varphi\to\psi})\wedge P_{\varphi}(\vec z_\varphi))\to P_{\psi}(\vec z_\psi)\}\cup \mathcal S^-(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\to\psi)  = \{(P_{\varphi}(\vec z_\varphi)\to P_{\psi}(\vec z_\psi))\to P_{\varphi\to\psi}(\vec z_{\varphi\to\psi})\}\cup \mathcal S^+(\varphi)\cup \mathcal S^-(\psi)$
			\item For quantified formulas $Qx\varphi(x)$ with $Q\in \{\forall,\exists\}$\\$\mathcal S^+(Qx\varphi(x)) = \{P_{Qx\varphi}(\vec z_{Qx\varphi})\to QxP_{\varphi}(\vec z_{\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^+(\varphi)\}$\\$\mathcal S^-(Qx\varphi(x))  = \{QxP_{\varphi}(\vec z_{\varphi})\to P_{Qx\varphi}(\vec z_{Qx\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^-(\varphi)\}$
		\end{itemize}
		and have $\mathcal S(\varphi) = \mathcal S^+(\varphi)\cup\mathcal S^-(\varphi)$.
	\end{definition}

@@

	\begin{definition}
		For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms of the form $P_\psi$. By slight abuse of notation we denote with $\vec z_\psi$ elements of the domain instead of variables. In the classical case have
		$$P_A^I(\vec z_A):\Leftrightarrow A^I(\vec z_A)$$
		and
		$$P_{\varphi\wedge\psi}^I(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\wedge P_{\psi}^I(\vec z_\psi)\indent P_{\varphi\vee\psi}^I(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\vee P_{\psi}^I((\vec z_\psi))$$$$ P_{\varphi\to\psi}^I(\vec z_{\varphi\to\psi}) :\Leftrightarrow (\neg P_{\varphi}^I(\vec z_{\varphi}))\vee P_{\psi}^I(\vec z_{\psi})$$
		$$P_{\forall x\varphi}^I(\vec z_{\forall x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for all $x\in M$}\}$$$$ P_{\exists x\varphi}^I(\vec z_{\exists x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for some $x\in M$}\}$$
		\\
		and for intuitionistic logic and some world $u$
		$$P_A^{I_u}(\vec z_A):\Leftrightarrow A^{I_u}(\vec z_A)$$
		and
		$$P_{\varphi\wedge\psi}^{I_u}(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\wedge P_{\psi}^{I_u}(\vec z_\psi)\indent P_{\varphi\vee\psi}^{I_u}(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\vee P_{\psi}^{I_u}((\vec z_\psi))$$$$ P_{\varphi\to\psi}^{I_u}(\vec z_{\varphi\to\psi}) :\Leftrightarrow(\neg P_{\varphi}^{I_w}(\vec z_{\varphi}))\vee P_{\psi}^{I_w}(\vec z_{\psi})\text{ for all $w\geq u$}$$
		$$P_{\forall x\varphi}^{I_u}(\vec z_{\forall x\varphi}) :\Leftrightarrow P_{\varphi}^{I_w}(\vec z_\varphi) \text{ for all $w\geq u$, $x\in M_w$}$$$$ P_{\exists x\varphi}^{I_u}(\vec z_{\exists x\varphi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi) \text{ for some $x\in M_u$}$$
		\\
	\end{definition}

@@

	\begin{lemma}
		For every formula $\varphi$ and structure $\mathcal M$
		$$\mathcal S(\mathcal M, \varphi)\models\mathcal S^+(\varphi)\cup S^-(\varphi)$$
	\end{lemma}

@@

	\begin{corollary}\label{equivalid}
		In both intuitionistic and classical logic
		\begin{itemize}
			\item $\varphi$ is satisfiable iff $\mathcal \bigwedge S^+(\varphi)\wedge P_\varphi(\vec z_\varphi)$ is.
			\item $\varphi$ is valid iff $\bigwedge\mathcal S^-(\varphi)\to P_\varphi(\vec z_\varphi)$ is.
		\end{itemize}
	\end{corollary}

	\section{IPC to CPC}

@@

	\section{IPC to QBF}

	It is well known that a polynomial time translation between QBF and IPC must exists, since both problems are PSPACE complete~\cite{garey1979computers, statman1979intuitionistic}. However giving an explicit translation from IPC to QBF can still be useful as good solvers exists for QBF but for IPC not so much. The translation from the last section will serve as a useful tool for this. We will not explain the semantics of QBF in depth. Intuitively just think that the interpretation of existentially quantified variables may depend on variables quantified above them.

	Fix some set $\mathcal S$ of formulas $\psi$ of the form $$A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$and$$\varphi = \bigwedge \mathcal S\to P$$
	and denote with $\mathcal F_\to$ the set of formulas of the form $(A\to B)\to C$. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a linear-size formula is: Instead of expressing validity at every node of $\mathcal M_T$ - which was done in the CPC translation - we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $F_\psi$ in the next definition handle the branching, i.e. express which path is considered.

	\begin{definition}
		For every propositional variable $X$ occurring in $\mathcal S$ and non-negative integer $n$ consider a new atom $X^n$ and for every formula $\psi\in\mathcal F_\to$ consider a new atom $F_\psi^n$. Let $\vec X^n$ range over all propositional variables $X^n$ and $\vec F^n$ range over all $F_\psi^n$. Define
		\begin{itemize}
			\item {\normalfont Valid}$(n)$ which encodes that $\vec F^n_\psi$ represents a valid next element of a sequence without repetition, i.e. if we interpret the $\vec F^i$ as bit-vectors, then $\vec F^n$ has exactly one bit set to $1$, indicating the formula at the $n$-th position of the sequence, and it is at a position that is $0$ in $\sum\{\vec F^i\:|\:i < n\}$.
			\item {\normalfont Persistent}$(n)$ which encodes that the persistency condition holds.
			\item {\normalfont Sat}$_{\mathcal S}(n)$ encoding that the formulas in $\mathcal S\setminus\mathcal F_\to$ hold at the $n$-th world of the path.
			\item {\normalfont Sat}$_{\mathcal F_\to}(n)$ encoding that the formula in $\mathcal F_\to$ that is represented by $\vec F^{n-1}$ holds.
		\end{itemize}
		Have $k = |\mathcal F_\to|$ and define$$\varphi^Q_{i} = \exists \vec X^i\forall \vec F^i\left(\text{\normalfont Persistent}(i)\wedge \text{\normalfont Sat}_{\mathcal S}(i)\wedge \text{\normalfont Sat}_{\mathcal F_\to}(i)\wedge\left(\text{\normalfont Valid}(i)\to \varphi^Q_{i+1}\right)\right)$$
		for $0 < i < k$ as well as the special cases
		$$\varphi^Q_{k} = \exists \vec X^k\left(\text{\normalfont Persistent}(k)\wedge \text{\normalfont Sat}_{\mathcal S}(k)\wedge \text{\normalfont Sat}_{\mathcal F_\to}(k)\right)$$
		for leafs and
		and $$\varphi^Q = \varphi_0^Q = \exists \vec X^0\forall \vec F^0\left(\neg P^0\wedge \text{\normalfont Sat}_{\mathcal S}(0)\wedge(\text{\normalfont Valid}(0)\to \varphi_1^Q)\right)$$for the root.
		Example encodings of the above formulas would be
		\begin{align*}
			\text{\normalfont Valid}(n) = &\left(\bigvee \{\mathcal F^n_\psi\:|\:\psi\in\mathcal F_\to\}\right)\wedge\left(\bigwedge \{\neg(F^n_{\psi_1}\wedge F^n_{\psi_1})\:|\:\psi_1\neq\psi_2\in\mathcal F_\to\}\right)\wedge\\&\wedge\left(\bigwedge\left\{\bigwedge\{F^i_\psi\to\neg F^n_\psi\:|\:i < n\}\:|\:\psi\in\mathcal F_\to\right\}\right)\\
			\text{\normalfont Persistent}(n) = & \bigwedge\{X^{n-1}\to X^n\:|\: X \text{ prop. variable with }X^{n-1}\in\vec X^{n-1}, X^n \in\vec X^{n}\}\\
			\text{\normalfont Sat}_{\mathcal S}(n) = &\bigwedge\left\{(A^n\circ B^n)\to C^n\:|\:(A\circ B)\to C\in \mathcal S\setminus\mathcal F_\to\right\}\wedge\\
			&\bigwedge\left\{A^n\to (B^n\circ C^n)\:|\:A\to (B\to C)\in \mathcal S\setminus\mathcal F_\to\right\}\\
			\text{\normalfont Sat}_{\mathcal F_\to}(n) = & \bigwedge\{F^{n-1}_\psi\to (A^n\to B^n)\to C^{n-1}\:|\:\psi = (A\to B)\to C\in\mathcal F_\to\}
		\end{align*}
	\end{definition}

@@

	\section{CQC to IQC}

	We now give an analogous transformation for first order logic. However our trick of lifting the sentence to first-order logic to encode the Kripke semantics no longer works in such a straightforward manner, since we already are in first-order logic. However we do it nonetheless! The domain of our classical model will feature on the one hand elements representing worlds in a Kripke frame and on the other hand the domain-elements from the Kripke model. We reconcile these notions by introducing a special binary predicate $E$, first considered in~\cite{baaz2006skolemization} and expanded onto in~\cite{iemhoff2010eskolemization}, where $E(x, u)$ encodes that $x$ is an element of the domain of the world $u$. We fix some signature $\Sigma$ for this section. To encode that some $n$-ary relation $A$ holds at a world $u$ we replace each $n$-ary relation symbol $A$ with a $n+1$-ary relation symbol $A^\#$, interpreting $A^\#(\vec x, u)$ as "$A(\vec x)$ holds at u". Furthermore we write $\vec E(\vec x, u)$ for $\bigwedge\{E(x_i, u)\:|\:x_i\in \vec x\}$.

	First of all recall that due to Lemma~\ref{equivalid} it is sufficient to consider sentences of the form $\bigwedge\mathcal S\to P$ where all formulas in $\mathcal S$ are of one of the forms

	$$\forall \vec z(A(\vec a)\to (B(\vec b)\wedge C(\vec c))), \forall \vec z((A(\vec a)\wedge B(\vec b))\to C(\vec c)),$$$$ \forall \vec z(A(\vec a)\to (B(\vec b)\vee C(\vec c))),
	\forall \vec z((A(\vec a)\vee B(\vec b))\to C(\vec c)),$$$$ \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c)),\forall \vec z(\forall xA(\vec a)\to B(\vec b)),$$$$ \forall \vec z(A(\vec a)\to\forall xB(b)), \forall \vec z(\exists xA(\vec a)\to B(\vec b)), \forall \vec z(A(\vec a)\to\exists xB(b))$$	
	As in the propositional case we will now encode the Kripke Semantics, this time not only the relation $\preceq$ but also $E$ has to be axiomatized. For that we use the following predicates:
	\begin{itemize}
		\item PartialOrder($\preceq$) encoding that $\preceq$ is a partial order.
		\item DomainSubset$(u, w)$ encoding that the domain at $u$ is a subset of that at $w$.
		\item World($u$) encoding that $u$ represents a world.
		\item DomainClosed($u$) which encodes that at $u$ the domain is closed under functions, e.g. contains all interpretations of constants.
		\item Persistent$(u, w)$ which encodes that persistency is satisfied between $u$ and $w$, i.e. for all predicates $A$ and domain elements $x$ with $A(x)$ at $u$ we have $A(x)$ at $w$.
	\end{itemize}
	Then analogously to the predicate case define
	\begin{align*}
		K(\varphi) = \:& \text{PartialOrder}(\preceq) \wedge \\
		& \forall u \forall w (u\preceq w\to \text{DomainSubset}(u, w)) \wedge\\
		& \forall u(\text{World(u)}\to \text{DomainClosed}(u))\wedge\\
		& \forall u\forall w (u\preceq w\to \text{Persistent}(u, w))
	\end{align*}
	Example encodings could be
	\begin{align*}
		\text{PartialOrder}(\preceq) = &\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{DomainSubset}(u, w) = &\:\forall z(E(z, u)\to E(z, w))\\
		\text{World}(u) = &\:\exists xE(x, u)\\
		\text{DomainClosed}(u) = &\:\bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f\in\Sigma$ is a function symbol}\}\\
		\text{Pesistent}(u, w) = &\:\bigwedge\{\forall\vec z(\vec A^\#(\vec z, u)\to A^\#(\vec z, w))\:|\:\text{$A\in\Sigma$ is a relation symbol}\}
	\end{align*}

	Using $E$ we then obtain $\mathcal S^\circ$ analogously to the predicate case by including formulas:

	\begin{itemize}
		\item $\forall \vec z\forall u(s\preceq u\to \vec E(\vec z, u)\to (A^\#(\vec a, u)\to (B^\#(\vec b, u)\circ C^\#(\vec c, u))))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z(A(\vec a)\to (B(\vec b)\circ C(\vec c)))\in\mathcal S$
		\item $\forall \vec z\forall u(s\preceq u\to\vec E(\vec z, u)\to (A^\#(\vec a, u)\circ B^\#(\vec b, u))\to C^\#(\vec c, u))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z((A(\vec a)\circ B(\vec b))\to C(\vec c))\in\mathcal S$
		\item $\forall \vec z\forall u(s\preceq u\to\vec E(\vec z, u)\to\forall w(u\preceq w\to A^\#(\vec a, w)\to B^\#(\vec b, w))\to C^\#(\vec c, u))$\\ for each $\psi = \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c))\in\mathcal S$
		\item  $\forall \vec z\forall u(s\preceq u\to\vec E(\vec z, u)\to \forall w(u\preceq w\to \forall x(E(x, w)\to A^\#(\vec a, w)))\to B^\#(\vec b, u))$\\for each $\forall \vec z(\forall xA(\vec a)\to B(\vec t_B))\in\mathcal S$.
		\item $\forall \vec z\forall u(s\preceq u\to\vec E(\vec z, u)\to A^\#(\vec a, u)\to \forall x(E(x, u)\to B^\#(\vec b, u)))$\\for each $\forall \vec t(A(\vec a)\to \forall xB(\vec b))\in\mathcal S$.
		\item $\forall \vec z\forall u(s\preceq u\to\vec E(\vec z, u)\to \exists x(E(x, u)\wedge A^\#(\vec z, u))\to B^\#(\vec b))$\\for each $\forall \vec z(\exists xA(\vec a)\to B(\vec b))\in\mathcal S$
		\item $\forall \vec z\forall u(s\preceq u\to\vec E(\vec z, u)\to A^\#(\vec b)\to \exists x(E(x, u)\wedge B^\#(\vec b, u)))$\\for each $\forall \vec z(A(\vec a)\to \exists xB(\vec b))\in\mathcal S$
	\end{itemize}

	Then $\varphi = \bigwedge\mathcal S\to P$ is intuitionistically valid iff
	$$\varphi^\circ= \text{World}(s)\to K(\varphi)\to \bigwedge S^\circ\to P^\#(s)$$
	is classically valid where $s$ is a new constant symbol. This was obvious in the propositional case but here it is more nuanced, so let's present a proof.

	\begin{proof}
		We proceed by translation of counter-examples. Suppose first we have a counter-example $\mathcal M = (M, I)$ to $\varphi^\circ$. As a Kripke frame $(W, \leq)$ take all $ W = \{m\in M\:|\:\text{ World}^I(m)\}$ let $\leq$ be $\preceq^I$ restricted to $W$. Then let $M_u = \{m\in M\:|\: E(m, u)\}$ and let $f^{I_u}$ be $f^I$ restricted to $M_u$ and $A^{I_u}(\vec x): \Leftrightarrow A^\#(\vec x, u)$. It is then a straightforward check of definitions that this defines a Kripke counter-model to $\varphi$.
